Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2015-12-11 paper/paper_acm_long.tex
add long version

In the definition of (a special case of) Giraud-Rezk-Lurie axiom given in
Section~\ref{sec:giraud-ax}, the colimit of the {\em \v{C}ech nerve}
plays a central role.
% 
Following the notion of (homotopy) limits of diagrams over graphs that
has been defined in homotopy type theory~\cite{lumsdaine}, we present
here a definition of colimits of diagrams overs graphs. 
%
The main difference between limits and colimits is that limits are
simply given by $\Sigma$-types, and thus exist already in traditional
type theory, whereas the situation is more complicated for colimits as
it requires the use of higher inductive types.

>>>>

In the definition of (a special case of) Giraud-Rezk-Lurie axiom given in
Section~\ref{sec:giraud-ax}, the colimit of the {\em \v{C}ech nerve}
plays a central role.
% 
Following the notion of (homotopy) limits of diagrams over graphs that
has been defined in homotopy type theory~\cite{lumsdaine}, we present
here a definition of colimits of diagrams overs graphs, presented in~\cite{sets_in_hott}. 
%
The main difference between limits and colimits is that limits are
simply given by $\Sigma$-types, and thus exist already in traditional
type theory, whereas the situation is more complicated for colimits as
it requires the use of higher inductive types.
